Supervised Reinforcement Learning with Partial States: \\ a Teaching Method for Action Selection for HRI

### 2017-07-26 paper.tex
Fixing typos

\maketitle
\begin{abstract}
%As robots will integrate human society, they will have to satify humans'
%expectations. However at the design time, it seems hardly possible to
%know in advance exactly all the behaviours expected from the robot. As such to
%be accepted in human society robots have to learn how to interact with humans.
    Social interacting is a complex task for which machine learrning holds particular promise. However, as no sufficiently
    accurate simulator of human interactions exists today, the learning of social interaction strategies has to happen online in the real
    world. Actions executed by the robot impact on humans, and as such
    have to be carefully selected, making it impossible to rely on random exploration. Additionally, no clear reward function exists for
    social interactions. This implies that classical approaches such as
    Reinforcement Learning cannot be directly applied for learning how to
    interact with the social world. As such we argue that
    robots will profit from human expertise and guidance to learn social
    interactions. And as the quantity of input a human can provide is limited,
    new methods have to be designed to use human input more efficiently. In this paper we describe a setpu in which We
    combine a framework called Supervised Progressively Autonomous Robot Competencies (SPARC), which
    allows safer online learning with Reinforcement Learning, with the use
    partial states rather than full states to accelerate generalisation and
    obtain more quickly a usable action policy.
\end{abstract}
%===============================================================================

@@

For a robot, interacting in the real world often requires taking in a diverse and large range of sensory inputs, which results in a high-dimensional sensory space. The robots then is required to select actions based on its current state in sensor space. However,
 parts of the state can be irrelevant to the current goal, and
 as such should not be taken into account when selecting the current action. Often, only a limited number of
 features in the space are important. To interact efficiently, a robot has to
 learn to identify these salient features and associate them with appropriate actions.

@@

In previous work~\cite{senft2015sparc,senft2017supervised}, we introduced the
Supervised Progressively Autonomous Robot Competencies (SPARC), a way to
teach a robot an action policy while interacting based on a human supervisor
intervening and correcting actions before they were executed by the robot. In this paper, we propose
to extend this approach to allow the supervisor to highlight features in the
environment relevant for the selected action. During the action selection
phase, the robot can compare these features, defined as partial states, with the
current state to select an action. The selected is presented to the human supervisor, who can either correct the action or approve it for execution.

@@

\subsubsection{Design decisions:}
Initial knowledge has to be use in the design of the algorithm, the
representation of the state and actions spaces and the reward funtion. For
example, only carefully crafted features allowed
Tesauro to improve its algorithm for Backgammon from a intermediate-level player
to super-human level~\cite{tesauro1995temporal}. Similarly, the design of
complex neural networks for state generalisation, the representation of actions
as motor primitives rather than raw motor angles or adding additional
information in the reward function have important impacts on the ability of
the robot to reach a successful policy~\cite{kober2013reinforcement}.

@@

To make RL applicable in high dimensional or continuous states, the algorithm
requires a way to generalise knowledge to unseen states. 
A classic approach is to use a feed-forward neural
network or to use deep reinforcement learning relying on deep neural
networks to learn a the value function. 
These approaches rely on having a large number of
datapoints to converge toward a good function approximator. However, 
 in many applications and especially in HRI, these amounts of data are not
available or obtainable due to practical constraints. Furthermore, human responses are often noisy and lack consistency, so methods are needed which can generalise from a low number of noise data points.

@@

SPARC has been shown to be compatible with RL in \cite{senft2017supervised},
and can also be easily combined with the approach presented in this paper using
partial states. For example, when selecting an action for the robot to be
executed, the supervisor can also select which features in the environment
should be selected as the partial state, and this associates the reward 
to this action in this partial state. Similarly, when an action is
proposed to the supervisor the features represented by the dimensions of the
closest partial state can be exposed to the supervisor as a way to explain why
this action has been selected. Facing this, the supervisor can: (1) not react,
allowing the action to be executed and associating a reward of +1 to the partial
state and the action proposed, (2) change the partial state to correct the features
related to this action or (3) cancel it, preventing the execution and associating a
reward of -1 to the partial state identified by the robot or the supervisor.

@@

As shown in Figures \ref{fig:game} and \ref{fig:gui}, the GUI is an augmented
version of the game itself, which can be use to make the robot move items on the
game by dragging them on the GUI or which can display actions proposed by the
robot with a cancel button to refuse an action. For example in
Figure~\ref{fig:gui} the robot proposes to move the eagle to the rat, and
highlight (as shown by blue circles) the eagle and the rat. This indicate that
features relevant to the eagle and the rat have been used to select this action.
\begin{figure}
        \centering
    \includegraphics[width=80mm]{./fig/proposition.png}
    \caption{Interface for the supervisor with an action being proposed, moving
        eagle to rat with highlight of eagle and rat.}
        \label{fig:gui}
\end{figure}

>>>>

\maketitle
\begin{abstract}
%As robots will integrate human society, they will have to satify humans'
%expectations. However at the design time, it seems hardly possible to
%know in advance exactly all the behaviours expected from the robot. As such to
%be accepted in human society robots have to learn how to interact with humans.
    Social interacting is a complex task for which machine learning holds particular promise. However, as no sufficiently
    accurate simulator of human interactions exists today, the learning of social interaction strategies has to happen online in the real
    world. Actions executed by the robot impact on humans, and as such
    have to be carefully selected, making it impossible to rely on random exploration. Additionally, no clear reward function exists for
    social interactions. This implies that classical approaches such as
    Reinforcement Learning cannot be directly applied for learning how to
    interact with the social world. As such we argue that
    robots will profit from human expertise and guidance to learn social
    interactions. And as the quantity of input a human can provide is limited,
    new methods have to be designed to use human input more efficiently. In this paper we describe a setup in which We
    combine a framework called Supervised Progressively Autonomous Robot Competencies (SPARC), which
    allows safer online learning with Reinforcement Learning, with the use
    partial states rather than full states to accelerate generalisation and
    obtain more quickly a usable action policy.
\end{abstract}
%===============================================================================

@@

For a robot, interacting in the real world often requires taking in a diverse and large range of sensory inputs, which results in a high-dimensional sensory space. The robot then is required to select actions based on its current state in sensor space. However,
 parts of the state can be irrelevant to the current goal, and
 as such should not be taken into account when selecting the current action. Often, only a limited number of
 features in the space are important. To interact efficiently, a robot has to
 learn to identify these salient features and associate them with appropriate actions.

@@

In previous work~\cite{senft2015sparc,senft2017supervised}, we introduced the
Supervised Progressively Autonomous Robot Competencies (SPARC), a way to
teach a robot an action policy while interacting based on a human supervisor
intervening and correcting actions before they were executed by the robot. In this paper, we propose
to extend this approach to allow the supervisor to highlight features in the
environment relevant for the selected action. During the action selection
phase, the robot can compare these features, defined as partial states, with the
current state to select an action. The selected action is presented to the human supervisor, who can either correct the action or approve it for execution.

@@

\subsubsection{Design decisions:}
Initial knowledge has to be used in the design of the algorithm, the
representation of the state and actions spaces and the reward funtion. For
example, only carefully crafted features allowed
Tesauro to improve its algorithm for Backgammon from a intermediate-level player
to super-human level~\cite{tesauro1995temporal}. Similarly, the design of
complex neural networks for state generalisation, the representation of actions
as motor primitives rather than raw motor angles or adding additional
information in the reward function have important impacts on the ability of
the robot to reach a successful policy~\cite{kober2013reinforcement}.

@@

To make RL applicable in high dimensional or continuous states, the algorithm
requires a way to generalise knowledge to unseen states. 
A classic approach is to use a feed-forward neural
network or to use deep reinforcement learning relying on deep neural
networks to learn a the value function. 
These approaches rely on having a large number of
datapoints to converge toward a good function approximator. However, 
 in many applications and especially in HRI, these amounts of data are not
available or obtainable due to practical constraints. Furthermore, human responses are often noisy and lack consistency, so methods are needed which can generalise from a low number of noisy data points.

@@

SPARC has been shown to be compatible with RL in \cite{senft2017supervised},
and can also be easily combined with the approach presented in this paper using
partial states. For example, when selecting an action for the robot to be
executed, the supervisor can also select which features in the environment
should be selected as the partial state, and this associates the reward 
to this action in this partial state. Similarly, when an action is
proposed to the supervisor the features represented by the dimensions of the
closest partial state for this action can be exposed to the supervisor as a way to explain why
this action has been selected. Facing this, the supervisor can: (1) not react,
allowing the action to be executed and associating a reward of +1 to the partial
state and the action proposed, (2) change the partial state to correct the features
related to this action or (3) cancel it, preventing the execution and associating a
reward of -1 to the partial state identified by the robot or the supervisor.

@@

As shown in Figures \ref{fig:game} and \ref{fig:gui}, the GUI is an augmented
version of the game itself, which can be use to make the robot move items on the
game by dragging them on the GUI or which can display actions proposed by the
robot with a cancel button to refuse an action. For example in
Figure~\ref{fig:gui} the robot proposes to move the eagle to the rat, and
highlight (as shown by blue circles) the eagle and the rat. This indicate that
features relevant to the eagle and the rat have been used to select this action.
\begin{figure}
        \centering
    \includegraphics[width=80mm]{./fig/proposition.png}
    \caption{Interface for the supervisor with an action being proposed, moving
        the eagle to the rat with highlight of the eagle and the rat.}
        \label{fig:gui}
\end{figure}
